Using Monte Carlo Algorithms to Achieve Resiliency \& Performance at Scale for Linear and Nonlinear Solver Applications

### 2016-01-25 doc/ecp/pres.tex
Adding preconditioning slides.

\begin{frame}{Polynomial Methods -- Summary}
  \begin{itemize}
    \item Using history length cutoff rather than weight cutoff can lead to
      large reductions in iteration counts
      \vfill
    \item A good approximation to a few terms in the Neumann series
      performs better than a statistically noisy approximation to
      full series
      \vfill
    \item Significant reduction in iteration counts are possible using
      alternate polynomials, but generally outweighed by increase in number
      of histories required
      \begin{itemize}
        \item May be very beneficial from resiliency and parallel efficiency
          standpoints
        \item Will be re-evaluated in future efforts
      \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Sparse Approximate Inverse Preconditioning}

>>>>

\begin{frame}{Polynomial Methods -- Summary}
  \begin{itemize}
    \item Using history length cutoff rather than weight cutoff can lead to
      large reductions in iteration counts
      \vfill
    \item A good approximation to a few terms in the Neumann series
      performs better than a statistically noisy approximation to
      full series
      \vfill
    \item Significant reduction in iteration counts are possible using
      alternate polynomials, but partially offset by increase in number
      of histories required
      \begin{itemize}
        \item May be very beneficial from resiliency and parallel efficiency
          standpoints
        \item Will be re-evaluated in future efforts
      \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Preconditioning}
  \begin{itemize}
    \item Preconditioning for Monte Carlo introduces nonstandard considerations
      \begin{itemize}
        \item Elements of preconditioned matrix must be explicitly available
        \item Goal of preconditioning is to reduce $\rho(\hat{\mathbf{H}})$,
          may not follow ``standard'' trends
      \end{itemize}
  \end{itemize}
  \vfill

  \begin{table}[!h]
  \centering
  \begin{tabular}{|c|c|c|c|}
  \hline
  \textbf{Block size} & \textbf{$\frac{nnz(H)}{nnz(A)}$}& $\rho(H)$
  &$\rho(\hat{H})$\\
  \hline
   3 & 1.4352 & $0.9804$ & $0.9531$\\
  \hline
   9 & 3.0220 & $0.9790$ & $0.9674$\\
  \hline
   33 & 9.8164 & $0.9783$  & $0.9774$\\
  \hline
  \end{tabular}
  \caption{$\rho(H)$ and $\rho(\hat{H})$ for advection--diffusion
  matrix with block diagonal preconditioning.}
  \label{tab:ifiss_block}
  \end{table}
\end{frame}

\begin{frame}{Preconditioning}
  \begin{itemize}
    \item Several options have been analyzed
      \begin{itemize}
        \item (Block) diagonal preconditioners, suitable for (block)
          diagonally dominant systems
        \item ILU-style preconditioners are possible, but require additional
          filtering to maintain sparsity in preconditioned system
        \item Approximate inverse preconditioning is attractive, forming
          preconditioned matrix only requires sparse matrix-matrix product
      \end{itemize}
  \end{itemize}

  \begin{table}[!h]
  \centering
  \begin{tabular}{|c|c|c|c|}
  \hline
  \textbf{Drop tolerance} & \textbf{$\frac{nnz(H)}{nnz(A)}$}& $\rho(H)$
  &$\rho(\hat{H})$\\
  \hline
   0.05 & 8.2797 & $0.9610$ & $1.0231$\\
  \hline
   0.01 & 33.1390 & $0.8668$ & $0.8279$\\
  \hline
  \end{tabular}
  \caption{$\rho(H)$ and $\rho(\hat{H})$ for 2D
  Laplacian with AINV preconditioning.}
  \label{tab:lap2d_ainv}
  \end{table}
